CODECHECK: An open-science initiative for the independent execution of computations underlying research articles

### 2021-01-12 codecheck-paper.tex
update annotated certificate AND METADATA

\subsection*{Annotated certificate}\label{annotated-certificate}

At the completion of each CODECHECK, a certificate is written that
states which outputs, i.e., numbers, figures and tables, from the 
original article could be reproduced by the codechecker.
This certificate is made openly
available so that all readers of the article can see which elements
have been reproduced.  The certificate also includes links to the code
and data used by the codechecker, allowing others to build on the
work.
The format of the certificates has evolved slightly during the
project, as we have learnt to automate different aspects of the
certification.

To demonstrate the typical contents of a certificate, in
Figure~\ref{fig:cert} we have annotated the first four out of ten
pages of the certificate \texttt{2020-012} \cite{cert-2020-012}.
The referenced article \cite{unwin_report_2020} describes the modelling COVID-19
across the USA.
%% TODO - has this been published yet?.  No, not yet... in review...
Figure~\ref{fig:cert}A shows the certificate number, and its DOI,
which points to the certificate as archived on Zenodo.
The CODECHECK logo is
attached to the certificate to denote successful reproduction.
Figure~\ref{fig:cert}B provides the key metadata about the check --
which paper was checked, who the authors and the codechecker were,
and when it was checked. Materials
relating to the codecheck are freely available via the Repository
link. This table is generated from machine readable text file, the
CODECHECK configuration file \texttt{codecheck.yml}.
The configuration file collects the core pieces of metadata surrounding
a check and enables current and future automation of workflows and 
meta-analyses.
Figure~\ref{fig:cert}C is a textual summary of how the codecheck was
performed, and any interesting findings.

Figure~\ref{fig:cert}D (page 2 of the certificate) shows a table that
lists the outputs that were generated from the codecheck (this is
termed the MANIFEST).  For each output, there is a comment stating
which figure/table it should be compared to in the original paper,
along with the size of the file.  On page 3 of the certificate,
Figure~\ref{fig:cert}E shows some more detailed notes from the
codechecker, in this case indicating what steps were needed to
initialize the environment and run the code.  This particular example
was quite long, taking about 17 hours to run.  Finally, on page 4 of
the certificate, we see the first output that was generated by the
codecheck (Figure~\ref{fig:cert}F).  In this case, the figure matches
figure~4 of \cite{unwin_report_2020}.
Subsequent pages of the certificate show other outputs (not shown here).

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/annotate-cert-crop.pdf}
  \caption{Annotated certificate 2020-012 \cite{cert-2020-012} (first four pages only).}
  \label{fig:cert}
\end{figure}

>>>>

\subsection*{Annotated certificate and check metadata}\label{annotated-certificate}

At the completion of each CODECHECK, the codechecker writes a certificate
stating which outputs, i.e.,~numbers, figures or tables, from the 
original article, could be reproduced by the codechecker.
This certificate is made openly
available so that all readers of the article can see which elements
have been reproduced and what limitations or issues were faced.
The certificate also includes links to the code
and data used by the codechecker, allowing others to build on the
work.
The format of the certificates has evolved slightly during the
project, as we have learnt to automate different aspects of the
certification, such as inserting figures into certificate documents
and managing core metadata surrounding a check.
The metadata is stored in a machine-readable structured file in YAML,
the CODECHECK configuration file \texttt{codecheck.yml}\footnote{
See technical specification of the CODECHECK configuration file at
\url{https://codecheck.org.uk/spec/config/latest/}}.
The configuration file enables current and future automation of workflows and
meta-analyses.

To demonstrate the typical contents of a certificate the the underlying
metadata, 
Figure~\ref{fig:cert} shows the first four out of ten
pages of the certificate \texttt{2020-012} \cite{cert-2020-012} with
annotations.
The referenced article \cite{unwin_report_2020} describes the modelling COVID-19
across the USA.
Figure~\ref{fig:cert}A shows the certificate number and its DOI,
which points to the certificate and any supplemental files on Zenodo.
The CODECHECK logo is
added for recognition and to denote successful reproduction.
Figure~\ref{fig:cert}B provides the key metadata as a table generated
from the \texttt{codecheck.yml} --
which paper was checked (title, DOI), who the authors and the codechecker 
were, when it was checked, and in which repository related material is
accessible.
Figure~\ref{fig:cert}C is a textual summary of how the CODECHECK was
performed, and any interesting findings.

Figure~\ref{fig:cert}D (page 2 of the certificate) shows a table that
lists the outputs that were generated from the check.
This table is generated from the manifest of output files in the CODECHECK
configuration file. The manifest lists output files with a short description.
The certificate's file table shows the file name, the description stating to
which figure/table each file should be compared to in the original paper, and
the size of the file.
Page 3 of the certificate,
as Figure~\ref{fig:cert}E shows, provides detailed notes from the
codechecker. In this particular example, the notes document what steps were 
needed to initialize the environment and run the code, and that the execution
took quite long to run -- about 17 hours.  Finally, on page 4 of
the certificate, we see the first output that was generated by the
CODECHECK (Figure~\ref{fig:cert}F).  In this case, the figure matches
figure~4 of \cite{unwin_report_2020}.
Subsequent pages of the certificate show other outputs and the computing
environment in which the certificate itself was created (not shown here).

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/annotate-cert-crop.pdf}
  \caption{Annotated certificate \texttt{2020-012} \cite{cert-2020-012} (first four pages only).}
  \label{fig:cert}
\end{figure}
